Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-23 paper/v2/paper-edited.tex
reduced to 14 pages

To ensure preferred paths are always obtained, for each router $r$ in the topology, the compiler sets a higher local preference for neighbors of a more-preferred node for $r$ in the PGIR. For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.

@@

After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on. In the compilation example all community tags can be removed, since there is never any ambiguity based on the router importing the route and the neighbor the route is being imported from. After removing the communities, the two rules at router $B$ are merged into a single rule.

@@

\begin{figure}[t!]
\begin{code}
  \Router{A}
    Match \PEER=C, \COMM=(3,2)
      Export \COMM \Arrow (4,2),
             \MED \Arrow 80, \PEER \Arrow W
  \Router{B}
    Match \PEER = C, \COMM = (-,2)
      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
             \MED \Arrow 81, \PEER \Arrow W
    Match \PEER = C, \COMM = (3,2)
      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
             \MED \Arrow 81, \PEER \Arrow W
  \Router{C}
    Match[LP=99] \PEER = E, \COMM = (-,2)
      Export \COMM \Arrow (-,2), \PEER \Arrow B
    Match \PEER = D, \COMM = (2,2)
      Export \COMM \Arrow (3,2), \PEER \Arrow A,B
  \Router{D}
    Match \REGEX{X + Y}
      Export \COMM \Arrow (2,2), \PEER \Arrow C
  \Router{E}
    Match \REGEX{Z}
      Export \COMM \Arrow (-,2), \PEER \Arrow C
  \end{code}
  \vspace{-2em}
  \caption{Abstract BGP router configurations. \label{fig:abgp-config}}
  \vspace{-1em}
\end{figure}

@@

\para{SDN languages}
\sysname{} was heavily influenced by SDN programming
languages such as NetKAT~\cite{netkat}, Merlin~\cite{foster:merlin}, FatTire~\cite{fattire},
as well as path queries~\cite{queries}.
Each of these languages is oriented around regular expressions, which
describe paths through a network, and predicates, which classify packets.
In particular, FatTire allows programmers to define sets of paths together
with a fault tolerance level (\IE, tolerate 1 or 2 faults)
and the compiler generates appropriate OpenFlow rules.
\sysname is more expressive as it allows users to specify preferences among
paths, and it generates distributed implementations that tolerate any number of faults.
Because FatTire generates data plane rules up front,
specifying higher levels of fault tolerance comes
at the cost of generating additional rules that tax switch memory.
In contrast, \sysname relies on distributed
control plane mechanisms to react to faults, which do not have additional memory cost.
Because of the differences in the underlying technology, the analyses
and compilation algorithms used in \sysname are quite different from
previous work on SDN.
Finally, in addition to using path-based abstractions
for intra-domain routing, \sysname uses them for inter-domain routing as
well, unlike existing SDN languages.

@@

\para{Configuration analysis}
The notion that configuring network devices is difficult and error-prone is not new.
In the past, researchers have tried to tackle this problem by analyzing existing
firewall configurations~\cite{fang,lumeta,margrave} and
router configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe,arc} and reporting errors or inconsistencies when they are detected.
Our research is complementary to these analysis
efforts.  We hope to eliminate bugs by using higher-level
languages and a ``correct-by-construction''
methodology.  By proposing that network administrators write configurations
at a high-level of abstraction, a whole host of low-level errors can be avoided and policy implementation can be simplified.

@@

We introduced \sysname, a language and compiler for implementing network-wide policies using a distributed set of devices running BGP. Propane allows operators to describe their policy naturally through high-level constraints on both the shape and relative preferences of paths for different types of traffic. When \sysname compiles a policy, the resulting BGP configurations are guaranteed to faithfully implement the centralized policy in a purely distributed fashion, regardless of any number of network failures. Applying \sysname to real-world networks showed that its language is expressive and its compiler is scalable.

>>>>

For each router $r$, the compiler sets a higher local preference for neighbors of a more-preferred PGIR node for $r$. For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.

@@

After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on. In the ABGP policy shown in Figure~\ref{fig:abgp-config}, all community tags can be removed, since there is never any ambiguity as to the current state of the PGIR based only on the current router importing the route and the neighbor from which the route is being imported.

@@

\begin{figure}[t!]
\begin{code}
  \Router{A}
    Match \PEER=C, \COMM=(3,2)
      Export \COMM \Arrow (4,2),
             \MED \Arrow 80, \PEER \Arrow W
  \Router{B}
    Match \PEER = C, \COMM = (-,2) or (3,2)
      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
             \MED \Arrow 81, \PEER \Arrow W
  \Router{C}
    Match[LP=99] \PEER = E, \COMM = (-,2)
      Export \COMM \Arrow (-,2), \PEER \Arrow B
    Match \PEER = D, \COMM = (2,2)
      Export \COMM \Arrow (3,2), \PEER \Arrow A,B
  \Router{D}
    Match \REGEX{X + Y}
      Export \COMM \Arrow (2,2), \PEER \Arrow C
  \Router{E}
    Match \REGEX{Z}
      Export \COMM \Arrow (-,2), \PEER \Arrow C
  \end{code}
  \vspace{-2em}
  \caption{Abstract BGP router configurations. \label{fig:abgp-config}}
  \vspace{-1em}
\end{figure}

@@

\para{SDN languages}
\sysname{} was heavily influenced by SDN programming
languages such as NetKAT~\cite{netkat}, Merlin~\cite{foster:merlin}, FatTire~\cite{fattire},
and path queries~\cite{queries}.
Each of these languages uses regular expressions to
describe paths through a network and predicates to classify packets.
In particular, FatTire allows programmers to define sets of paths
with a fault tolerance level (\IE, tolerate 1 or 2 faults)
and the compiler generates appropriate OpenFlow rules.
\sysname is more expressive as it allows users to specify preferences among
paths, and it generates distributed implementations that tolerate any number of faults.
Because FatTire generates data plane rules up front,
specifying higher levels of fault tolerance comes
at the cost of generating additional rules that tax switch memory.
In contrast, \sysname relies on distributed control plane mechanisms to react to faults, which do not have additional memory cost.
Because of the differences in the underlying technology, the analyses
and compilation algorithms used in \sysname are quite different from
previous work on SDN.
Finally, in addition to using path-based abstractions
for intra-domain routing, \sysname uses them for inter-domain routing as
well, unlike existing SDN languages.

@@

\para{Configuration analysis}
The notion that configuring network devices is difficult and error-prone is not new.
In the past, researchers have tried to tackle this problem by analyzing existing
%firewall configurations~\cite{fang,lumeta,margrave} and
router configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe,arc} and reporting errors or inconsistencies when they are detected.
Our research is complementary to these analysis
efforts.  We hope to eliminate bugs by using higher-level
languages and a ``correct-by-construction''
methodology. Writing configurations at a high level of abstraction simplifies policy implementation and prevents a whole host of low-level errors.
%By proposing that network administrators write configurations
%at a high-level of abstraction, a whole host of low-level errors can be avoided and policy implementation can be simplified.

@@

We introduced \sysname, a language and compiler for implementing network-wide policies using a distributed set of devices running BGP. Propane allows operators to describe their policy through high-level constraints on both the shape and relative preferences of paths for different types of traffic. When \sysname compiles a policy, the resulting BGP configurations are guaranteed to 
%remain policy-compliant
implement the centralized policy in a distributed fashion, 
regardless of any number of network failures. Applying \sysname to real-world networks showed that its language is expressive and its compiler is scalable.
